P259: Gene set enrichment analysis (GSEA)

### 2021-05-19 3.P259.pDC_GSEA.Rmd
Update Broad gene sets to v7.4

```{r h, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/h.all.v7.1.symbols.gmt")
```

#### Curated gene sets (C2)

```{r c2, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/c2.all.v7.1.symbols.gmt")
```

#### GO gene sets (C5)

```{r c5, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/c5.all.v7.1.symbols.gmt")
```

@@

```{r echo=FALSE, message=FALSE}
#Load results for faster knitting
h_GSEA.result <- read_csv("results/GSEA_FoldChange/h_GSEA.result.csv")
c2_GSEA.result <- read_csv("results/GSEA_FoldChange/c2_GSEA.result.csv")
c5_GSEA.result <- read_csv("results/GSEA_FoldChange/c5_GSEA.result.csv")
```

@@

>>>>

```{r h, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/h.all.v7.4.symbols.gmt")
```

#### Curated canonical pathway gene sets (C2:CP)

```{r c2, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/c2.cp.v7.4.symbols.gmt")
```

#### GO biological procress gene sets (C5:GO:BP)

```{r c5, warnings=FALSE, message=FALSE, eval=FALSE}
GSEA(gene_list = gene.ls, 
     gmt_file="data_clean/Broad_gmt/c5.go.bp.v7.4.symbols.gmt")
```

@@

```{r echo=FALSE, message=FALSE}
fdr.cut <- 0.1
#Load results for faster knitting
h_GSEA.result <- read_csv("results/GSEA/h_GSEA.result.csv")
c2_GSEA.result <- read_csv("results/GSEA/c2_GSEA.result.csv")
c5_GSEA.result <- read_csv("results/GSEA/c5_GSEA.result.csv")

#Combine and filter signif
GSEA.all <- bind_rows(h_GSEA.result,c2_GSEA.result,c5_GSEA.result)
#list all terms with at least 1 significant treatment contrast
term.OI.t <- GSEA.all %>% 
  filter(fgsea.FDR <= fdr.cut & gage.FDR <= fdr.cut) %>% 
  filter(group %in% c("AntiIL5_nonenone_none", "AntiIL5_HRVnone_HRV",
                      "EOSsupp_nonenone_none", "EOSsupp_HRVnone_HRV")) %>% 
  distinct(pathway) %>% unlist(use.names=FALSE)

#list all terms with at least 1 significant virus contrast 
term.OI.v <- GSEA.all %>% 
  filter(fgsea.FDR <= fdr.cut & gage.FDR <= fdr.cut) %>% 
  filter(group %in% c("none_HRVnone_none","AntiIL5_HRVAntiIL5_none",
                      "EOSsupp_HRVEOSsupp_none")) %>% 
  distinct(pathway) %>% unlist(use.names=FALSE)

#Find terms with both t and v cutoffs
term.OI <- intersect(term.OI.t, term.OI.v)

GSEA.signif <- GSEA.all %>% 
  filter(pathway %in% term.OI)
```

@@

```{R echo=FALSE}
GSEA.signif %>% 
  select(pathway, group, fgsea.FDR,fgsea.NES) %>% 
  separate(pathway, into=c("set","pathway"), sep="_", extra = "merge") %>% 
  select(set, pathway, group, fgsea.FDR,fgsea.NES) %>% 
  arrange(set, pathway, fgsea.NES) %>% 
  kable() %>%
kable_styling(bootstrap_options = "striped", full_width = FALSE) %>% 
  collapse_rows(1:2, valign = "top")
```
